Rank Recovery

### 2020-11-12 output_scripts/rank_recovery.Rmd
add ranks for m1 and m2 also and some code to tidy this up

@@

training_data
### need score (1) for all of these, along with the row number

>>>>

Similarly, we can compute the Spearman rank correlation between each of these 
models and the truth.

```{r some code to summarise these, eval = FALSE}
### compute spearman rank
truth <- output_rank$truth
output_rank %>% 
  select(m1:isi) %>%
  map( ~cor.test(truth, .x,
                method = "spearman")$estimate  ) %>%
  enframe() %>%
  unnest(cols = c(value))

output_rank2 <- output_rank
output_rank2$sim <- 2
output_rank2

bind_rows(output_rank, output_rank2) %>%
  group_by(sim) %>%
  select(m1:isi) %>%
  map( ~cor.test(truth, .x,
                 method = "spearman")$estimate  ) %>%
  enframe() %>%
  unnest(cols = c(value))

sims_list <- list()

sims_list[[1]] <- output_rank
sims_list[[2]] <- output_rank2

spear <- function(sim_data) {
  truth <- sim_data$truth
  sim_data %>%
    select(m1:isi) %>%
    map( ~cor.test(truth, .x,
                   method = "spearman")$estimate  ) %>%
    enframe() %>%
    unnest(cols = c(value))
}

map_dfr(sims_list, spear) # in a nice long format
```

@@

# training_data
### need score (1) for all of these, along with the row number
